---
title: "Mid-Term- Project-Redesign-Code"
author: "Shwetha-Shameema-Aniritha"
date: "2022-10-06"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---
1. Bad-Graph

```{r}
            # Install png package
library("png")
library("patchwork")  
my_image <- readPNG("C:\\Users\\aniri\\OneDrive\\Documents\\graphbad2.png", native = TRUE)
ggp_image <-                    # Combine plot & image
  inset_element(p = my_image,left = 0.5,
                bottom = 0.55,
                right = 0.95,
                top = 0.95
                )
ggp_image   

```

2.Dot-Plot

```{r}
library(ggplot2)
library(plotly)
library(readr)

Data_df <- read_csv("STAT-515-Midtermdataset.csv")
a <- ggplot(Data_df , aes(x = code, y = Rank)) +
  xlab("States") +
  ylab("Ranking") +
geom_point() 
a  + theme(axis.text = element_text(size= 6, vjust = -1,colour = "black"))

```


3. Bar-Graph

```{r}

library(plotly)
library(readr)
library(ggplot2)

Data_df <- read_csv("STAT-515-Midtermdataset.csv")
 #BAR GRAPH 1
plot_ly(
  data = Data_df,
  x = ~code,
  y = ~Rank,
  type = "bar",
  color = ~code,
  colors = c("red", "blue", "black", "#32a852", "#c10dd1")
)

#BAR GRAPH 2
plot_ly(
  data = Data_df,
  x = ~code,
  y = ~onemillion_last,
  type = "bar",
  color = ~code,
  colors = c("green","yellow")
)%>%layout(
  title = "HOW LONG $1 MILLION WOULD LONG LAST",
  xaxis = list(title="STATES",categoryorder = "total descending"),
  yaxis = list(title = "YEARS")
)
```

4.MicroMap

```{r}
library(micromapST)
library(tidyverse)

millionWill <- read.csv(file = "STAT-515-Midtermdataset.csv",header=T, as.is=TRUE)
str(millionWill)

type=c('mapcum','id','dot','dot')
lab1=c('','','Cost of','one million')
lab2=c('','','Living Index','will last')
lab3=c('','','Dollars','Years')
col1=c(NA,NA,'CostofLiving','onemillion_last')
col2=c(NA,NA,NA,'Years.Months')
refVals=c(NA,NA,NA,0)

panelDesc <- data.frame(type,lab1,lab2,lab3,col1,col2,refVals)

fname = "1MillionWill.pdf"
pdf(file = fname,width = 7.5,height = 10)

micromapST(millionWill,
           panelDesc,
           rowNamesCol = 'State',
           rowNames = 'full',
           sortVar = 'onemillion_last', ascend = FALSE,
           title = c("Can you Retire on 1 Million?",
           "Here is What You Need to Know..."),
           ignoreNoMatches = FALSE)

```



5.Plot 


```{r}

library(dplyr)
library(readr)
library(maps)
library(plotly)


#loading data
Data_df <- read_csv("STAT-515-Midtermdataset.csv") %>%
mutate(hover = paste0("STATE:",' ',State,'\n',"RANK:",' ',Rank,'\n',"ANNUAL_LIVING_COST:",' ',Annual_expenditure_Costofliving,'\n',"Year.Month:",' ',onemillion_last ))



graph = plot_geo(Data_df, 
                        locationmode = "USA-states",
                 colors = 'Spectral'
                       ) %>%
  add_trace(locations = ~code,
            z = ~Rank ,
            color = ~Rank,
            text = ~hover,
            hoverinfo = 'text'
             
            )%>%
  add_trace(type = "scattergeo",
            locationmode = 'USA-states',
             locations =~code,
            mode = "text",
            text = ~code,
            textfont = list(color = rgb(0,0,0), size = 12)
            )%>%
  layout(geo = list(scope = 'usa'))%>%
  layout( title = "How Long $1 Million Will Last in Retirement in Every State"
        )%>%
 config(displayModeBar = FALSE)
  


graph

```
Figure 5: The Representation of Entire Interative  US map to know how long 1 million will last after Retirement in every satae.


6. Projecting Top 4 countries with Low Rank and High Cost of Living



```{r}
library(usmap)
library(dplyr)
library(maps)
library(plotly)

USA <- read.csv(
  file="STAT-515-Midtermdataset.csv",
  header=T, as.is=TRUE)
USA <- USA[order(USA$State),]
USA$fips = statepop$fips
USA$abbr = statepop$abbr

  
h<-plot_usmap(data = USA, values = "Rank", include = c("CA","OR","NY","HI"),labels = TRUE) + 
  scale_fill_distiller('Rank', palette="Spectral")+
  labs(title = "Top 4 Region", subtitle = "Low Rank Sataes where Cost of living High") +
  theme(legend.position = "right")
h
```
Figure 7: Shows The top-4 Region in USA which has High-Cost of living and Rank that does not suit for living after Retirement.  

7. Projecting Top 4 countries with High Rank and High Cost of Living.


```{r}
library(usmap)

USA <- read.csv(
  file="STAT-515-Midtermdataset.csv",
  header=T, as.is=TRUE)
USA <- USA[order(USA$State),]
USA$fips = statepop$fips
USA$abbr = statepop$abbr
l<- plot_usmap(data = USA, values = "Rank", include = c("MS","AR","TN","KS"),color = "Red",labels = TRUE) + 
  scale_fill_distiller('Rank', palette="Spectral")+
  labs(title = "TOP 4 Region", subtitle = " Rank Sataes where Cost of living Low") +
  theme(legend.position = "right")
l
```
Figure 7: Shows The top-4 Region in USA which has low-Cost of living and Rank that does may suit for living after Retirement. 
